\documentclass[]{cls}
\usepackage{fontspec}
\def\kt{\vspace*{2pt}\textsc{TECHNOLOGIES:\,}}
\begin{document}

\namesection{Devan}{Patel}{
\faEnvelope \, devanppatel@gmail.com \textbullet{} \faPhone \, 954.695.2250 \textbullet{} \faGithub \, devanp92 \textbullet{} \faLinkedin \, \href{https://www.linkedin.com/in/devanp92}{devanp92} \textbullet{} \faGlobe www.devanpatel.me \vspace{\topsep}

Computer Science graduate with a strong math and programming background looking for a software engineering role.}


\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 
\sectionsep
\subsection{University of Florida}
\descript{B.S. Computer Science Engineering \& Mathematics}
\location{Gainesville, FL}
College of Engineering \\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
Java \textbullet{}
C/C++ \textbullet{}
Javascript \textbullet{}
Python \textbullet{}
Ruby \textbullet{}
Shell
\sectionsep
\subsection{Web}
HTML5 \textbullet{}
CSS3 \textbullet{}
JQuery \textbullet{}
ES6 \textbullet{}
Angular.js \textbullet{}
Node.js \textbullet{}
Sails.js \textbullet{}
Rails
\sectionsep
\subsection{Database}
MonogoDB \textbullet{}
PostgreSQL \textbullet{}
CouchDB \textbullet{}
Redis \textbullet{}
Neo4J \textbullet{}
SQL \textbullet{}
\sectionsep
\subsection{Version Control}
Git \textbullet{}
Subversion \textbullet{}
Mercurial

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Computer Science}
Computer Network Fundamentals\\
Operating Systems\\
Data Structures \& Algorithms\\
Object Oriented Principles\\
Design Patterns\\
Database \& Information Systems\\
Concurrent Programming\\
Computer Organization\\
Digital Logic
\sectionsep
\subsection{Mathematics}
Analysis\\
Complex Analysis\\
Analysis\\
Abstract Algebra\\
Combinatorics $\mathrm{I \& II}$\\
Combinatorial Theory\\
Multivariable Calculus\\
Probability Theory\\
Numerical Analysis

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\sectionsep

\runsubsection{Goldman Sachs Group, Inc.}
\descript{| Technology Analyst Intern }
\location{May 2013 – August 2013 | New York, NY}
\vspace{\topsep}
\begin{tightemize}
\item Database performance monitoring: Created a test suite to analyze, monitor and visualize database performance to predict anomalies. 
\item Designed API to integrate with Global Operations Technology teams cross-divisional.
\end{tightemize}
\kt Java, Groovy, R, DB2, JMX, JUnit, Maven, JIRA

\sectionsep

\runsubsection{Florida Institute for Cyber Security}
\descript{| Researcher }
\location{Spring 2014 - Current | Gainesville, FL}

\begin{tightemize}
\item Analyzed SSL/TLS Certificate Authority alternatives robustness and integrity to improve the certificate validation process.
\item Build module to capture results from passive network scans from over 4 million hostnames and integrated with FICS' Certshim application.
\end{tightemize}
\kt C, Python, Node.js, Angular.js, D3.js, Vagrant/Puppet/Chef, HTML, CSS, SQLite3, MongoDB, Github, Heroku

\sectionsep

\runsubsection{Nodeware, Inc.}
\descript{| Software Engineer }
\location{Spring 2013 - present | Coral Springs, FL}
\begin{tightemize}
\item Consulting clients by developing applications specializing in SOA architectures. 
\item Operated closely with senior management at client companies to develop solutions to meet their business goals.
\item Collaborated with senior developers to redesign and implement products to increase revenue growth.
\end{tightemize}
\kt Ruby, Rails, Javascript, CSS, HTML5, PostgreSQL, Node.js, Angular.js, RSpec, Heroku, Git

\sectionsep

\runsubsection{Rokk3r Labs}
\descript{| Startup Fellow }
\location{May 2014 - August 2014 | Miami Beach, FL}
\begin{tightemize}
\item Developed a proprietary full-stack enterprise agile project management tool to be used by all divisions.

\item Conducted technology analysis for machine learning, computer vision, and big data to design a prototype for several clients investment pitches.

\end{tightemize}
\kt Angular.js, Sails,js, Node.js, Javascript, CSS, HTML5, MongoDB, Redis, Selenium, Mocha, Jasmine, Heroku, Git



\sectionsep

\runsubsection{Pinch a Penny, Inc.}
\descript{| Freelance Software Engineer}
\location{May 2013 - December 2013 | Coconut Creek, FL}
\begin{tightemize}
\item Developed proprietary Android application that enables pool servicers to connect to remote PostgreSQL database allowing CRUD functionality on client information.

\item Created Groovy command line scripts for retrieving customer information and sending to servicers via SMS messaging, increase servicing volume by 10\%.

\end{tightemize}
\kt Python, Java, Groovy, PostgreSQL, HTML5, CSS, Android, JUnit, Apache Email Commons, Git

\end{minipage} 
\end{document}
